Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-03-16 fertile.Rmd
more edits

When considered in combination, these sources provide a well-rounded picture of the components important to research reproducibility. Using this literature as a guideline, we identify several key features of reproducible work to focus on:

@@

Much of the available literature focuses on file structure, organization, 
and naming, and **fertile**'s features are consistent with this. The 
*ideal* file structure is not agreed upon by academics, though there are 
some recommendations focused on R that are available.@marwick2018packaging
provides the framework for file structure that **fertile** is based on: a 
structure similar to that of an R package [**Cite Hadley's Writing R 
Packages and the R Core Team's Writing R Extensions**], with an `R` 
folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

@@

[**Clarify why fertile comes in handy**]
Additionally, with the focused nature of these packages comes added complexity. The functions in these packages are often quite complex to use, and many steps must be completed to achieve the required reproducibility goal. This cumbersome nature means that most reproducibility packages currently available are not easily accessible to users near the beginning of their R journey, nor particularly useful to those looking for quick and easy reproducibility checks. 
[**Note that our recommendations are opinionated**]

@@

In addition to the interactive log, users can access a render log, [**define this**] which contains much of the information used to create the output for `proj_analyze()` using the function `render_log_report()`.

>>>>

When considered in combination, these sources provide a well-rounded picture of the components important to research reproducibility. Using this literature as a guideline, we identify several key features of reproducible work to focus on. These recommendations are opinionated---due to the lack of agreement on which components of reproducibility are most important, we select those that are mentioned most often, as well as some that are mentioned less but that we view as important.

@@

Much of the available literature focuses on file structure, organization, 
and naming, and **fertile**'s features are consistent with this. The 
*ideal* file structure is not agreed upon by academics, though there are 
some recommendations focused on R that are available. @marwick2018packaging
provides the framework for file structure that **fertile** is based on: a 
structure similar to that of an R package [**Cite Hadley's Writing R 
Packages and the R Core Team's Writing R Extensions**], with an `R` 
folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

@@

Additionally, with the focused nature of these packages comes added complexity. The functions in these packages are often quite complex to use, and many steps must be completed to achieve the required reproducibility goal. This cumbersome nature means that most reproducibility packages currently available are not easily accessible to users near the beginning of their R journey, nor particularly useful to those looking for quick and easy reproducibility checks.

@@

In addition to the interactive log, users can access a render log, which is created by running all of the `.R` and `.Rmd` files within a project in order to collect information on packages, file paths, and file structure used to create the output for `proj_analyze()`. This log can be accessed with the function `render_log_report()`.
